Concurrent Programming with Harmony

### 2020-08-05 book/paper.tex
Latest

  description={is a process that cannot change the state unless another
    process changes the state first.  For example, a process that is waiting
    for a lock to become available}

@@

We call a process \emph{blocked}
\index{blocked process}%
if the process can only change the state if another process changes
the state first.
A process trying to
acquire a test-and-set spinlock held by another process is a good example
of a process being blocked.
The only way forward is if the other process releases the lock.

>>>>

  description={is a process that cannot change the state or terminate or
      can only do so after another process changes the state first.
      For example, a process that is waiting for a lock to become available}

@@

We call a process \emph{blocked}
\index{blocked process}%
if a process cannot change the state or terminate or can only do so if
another process changes the state first.
A process trying to
acquire a test-and-set spinlock held by another process is a good example
of a process being blocked.
The only way forward is if the other process releases the lock.
A process that is in an infinite loop is also considered blocked,
although Harmony can often detect infinite loops specifically.
